Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-19 paper.tex
Cite weak magnetism and pinched spectra

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  \caption{Mean free paths
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$).
    In the fluid rest frame these are given by
    $(\chi^*_a)^{-1}$ for the absorption
    and $(\chi_s)^{-1}$ for elastic scattering interactions.
    Note that elastic scattering opacities are identical across species
    below energies at which weak magnetism plays a role.
    In this data they are exactly identical
    because we have turned off weak magnetism in our opacity calculations
    in order to compare our results with the historical literature.
    Computed using \lstinline{NuLib}.
  }
  \label{fig:mfps-50km}
\end{figure}

@@

\subsection{Inelastic scattering}
\label{ssec:sources_si}
Neutrino scattering off of electrons is inelastic, changing the
magnitude and direction of the species' momenta.
A similar formalism to the above could be used to derive source terms
for inelastic scattering.
\todo{compare relative amounts of inelastic to elastic scattering}
We save that for future work, pointing out here that inelastic scattering
treated this way is very sensitive to the energy-dependence of
the background field.

\subsection{Thermal pair annihilation and production}
\label{ssec:sources_pp}
We do not include thermal pair processes within the above formalism,
but as mentioned in App.~\ref{ssec:sources_ae}, we do include
these processes in an effective absorption opacity for $\mu$ and $\tau$
neutrinos and antineutrinos. \lstinline{NuLib} follows
\cite{brue1985-core_collapse,burr2006-neutrino_opacities}
by computing the emissivity of the pair processes in
\todo{describe better}
Tab.~\ref{tab:neutrino_processes}, and applying Kirchoff's law,
Eqn.~\ref{eqn:kirchoffs_law}, to convert this to an opacity.
We only use this effective opacity for heavy-lepton neutrinos because
it is subdominant to the true absorption opacity for
$\nu_e$ and $\bar{\nu}_e$.

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  \caption{Mean free paths
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$).
    In the fluid rest frame these are given by
    $(\chi^*_a)^{-1}$ for the absorption
    and $(\chi_s)^{-1}$ for elastic scattering interactions.
    Note that elastic scattering opacities are identical across species
    below energies at which weak magnetism plays a role \cite{horo2002-weak_mag}
    (?).
    In this data they are exactly identical
    because we have turned off weak magnetism in our opacity calculations
    in order to compare our results with the historical literature.
    Computed using \lstinline{NuLib}.
  }
  \label{fig:mfps-50km}
\end{figure}

@@

\subsection{Inelastic scattering}
\label{ssec:sources_si}
Neutrino scattering off of electrons is inelastic, changing the
magnitude and direction of the species' momenta.
\todo{cite \cite{keil2003-pinched_spectra} or someone}
A similar formalism to the above could be used to derive source terms
for inelastic scattering.
\todo{compare relative amounts of inelastic to elastic scattering}
We save that for future work, pointing out here that inelastic scattering
treated this way is very sensitive to the energy-dependence of
the background field.

\subsection{Thermal pair annihilation and production}
\label{ssec:sources_pp}
We do not include thermal pair processes within the above formalism,
\todo{explain this choice, and cite \cite{keil2003-pinched_spectra} or someone}
but as mentioned in App.~\ref{ssec:sources_ae}, we do include
these processes in an effective absorption opacity for $\mu$ and $\tau$
neutrinos and antineutrinos. \lstinline{NuLib} follows
\cite{brue1985-core_collapse,burr2006-neutrino_opacities}
by computing the emissivity of the pair processes in
\todo{describe better}
Tab.~\ref{tab:neutrino_processes}, and applying Kirchoff's law,
Eqn.~\ref{eqn:kirchoffs_law}, to convert this to an opacity.
We only use this effective opacity for heavy-lepton neutrinos because
it is subdominant to the true absorption opacity for
$\nu_e$ and $\bar{\nu}_e$.
